Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-25 draft.tex
write up

>>>>

In order to see other properties of the operators, we apply a different change of variables. 
Let us write this in detail for the operator $R_{\ell}$. 
We substitute $y$ by the new variable $a=y+t(x-y)$.
Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\&= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
\end{align*}
Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
Whence $t = \left( 1/s-1 \right)^{-1}$.
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
    \chi_{\Omega}\left(a\right) 
    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
    \\
    &= 
    .
\end{align*}

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_{1}^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel:
\begin{align*}
    \Bogov_{\ell} u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
$a = y + t(x-y)$
$s = \frac{t}{t-1}$
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Bogov_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.

From this form of $\Bogov_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Bogov_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Bogov_{\ell} u$ is ${C^\infty}$ on 
$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
$\Bogov_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
Thus if $\Omega$ is open and starlike with respect to $B$, then   
$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\overline\Omega$. 
The fact that $\Bogov_{\ell}$ indeed maps 
${C^\infty_c}(\bbR^n,\Alt^\ell)$ to ${C^\infty_c}(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.

\subsection{Homotopy relations}

Cartan's formula for the Lie derivative of a differential form with respect to a vector field can be written as
$$
  \frac{d}{dt}F^*_t u = F^*_t \left(d(X_t\lrcorner u) + X_t\lrcorner du\right)\;,
$$
where $F^*_t$ denotes the pull-back by the flow $F_t$ associated with the vector field $X_t$. Here we consider the special case of the dilation flow with center $a$
$$
  F_t(x) = a+t(x-a) \quad\text{ with vector field } X_t=x-a\;,
$$
which gives a pull-back of
$$
  F^*_t u(x) = t^\ell \,u\left(a+t(x-a)\right) \quad \text{for an $\ell$-form } u \;.
$$
This leads to the formula
\begin{equation}
\label{eq:Cartan}
 \frac{d}{dt}(t^\ell u\left(a+t(x-a)\right) =
    d\Bigl(t^{\ell-1}(x-a)\lrcorner u\left(a+t(x-a)\right)\Bigr) +
    t^{\ell}(x-a)\lrcorner du\left(a+t(x-a)\right)
\end{equation}
which can also be verified elementarily from the formulas we gave in Section~\ref{S:notation}.

Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
we find the homotopy relations, valid for all $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$ 
\begin{equation}
\begin{aligned}
\label{eq:dR+Rd=1}
 dR_{\ell} u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
 R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
 dR_nu &=u &&(\ell=n)\;.
\end{aligned}
\end{equation}
One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Bogov_{\ell}$ directly. The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Bogov_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved. Here is what one obtains for $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$:
\begin{equation}
\begin{aligned}
\label{eq:dT+Td=1}
  d\Bogov_{\ell} u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
  T_1 du &= u \; &&(\ell=0)\;;\\
 dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
\end{aligned}
\end{equation}
Here we consider $\chi_{\Omega}$ as an element of ${C^\infty_c}(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.

The formulas for the endpoints $\ell=0$ and $\ell=n$ correspond to the two extended de Rham complexes without boundary conditions and with compact support, see \eqref{eq:edRwobc} and \eqref{eq:edRwcs}. To see this, let us extend the definition of the exterior derivative by writing $\overline d$ for all the mappings of the complex
$$
 0 \to\bbR\to^\iota{C^\infty}(\overline\Omega,\Alt^0) \to^d {C^\infty}(\overline\Omega,\Alt^1)
 \to^d\cdots \to^d {C^\infty}(\overline\Omega,\Alt^n) \to 0
$$ 
and $\underline d$ for all the mappings of the complex
$$
 0 \to {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^0) \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^1) \to^d\cdots
 \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^n) \to^{\iota^*} \bbR \to 0
$$
where $\iota$ is the inclusion mapping for constant functions and 
$\iota^*=(\star\iota)'$ denotes the integral $u\mapsto\int\!u$ for $n$-forms.

If we correspondingly extend the definitions of $R_{\ell}$ and $\Bogov_{\ell}$ by
$$
\begin{aligned}
  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
  R_{n+1} &:=0\,,\\
  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
  T_0 &:= 0\,,
\end{aligned}
$$
then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
\begin{equation}\label{eq:R&T&d}
 \overline d\,R_{\ell} u + R_{\ell+1} \,\overline d u  = u
 \quad \text{ and }\quad
 \underline d\,\Bogov_{\ell} u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
  0\le\ell\le n.
\end{equation}
